---
title: "Transportation of Goods"
author: "Hannah Laws"
date: "April 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fpp2)
library(dplyr)
library(seasonal)
library(tseries)
library(urca)
m<-read.csv("fredgraph.csv")
# https://fred.stlouisfed.org/series
```



With the rise in online shopping, the different methods of transporting goods has undergone changes due to increased demand. The different methods of transportation look into international travel over seas, by plane, by truck, and by train.
```{r}
#cleaning up the data
ts_w<-ts(m$WATERBORNED11_NBD20000101, frequency = 12, start = c(2000,1))
ts_a<-ts(m$AIRRTMFMD11_NBD20000101, frequency = 12, start = c(2000,1))
ts_t<-ts(m$TRUCKD11_NBD20000101, frequency = 12, start = c(2000,1))
ts_r<-ts(m$RAILFRTCARLOADSD11_NBD20000101, frequency = 12, start = c(2000,1))



ts_w_train <- window(ts_w, start = 2000, end = 2013)
ts_a_train <- window(ts_a, start = 2000, end = 2013)
ts_t_train <- window(ts_t, start = 2000, end = 2013)
ts_r_train <- window(ts_r, start = 2000, end = 2013)
```




```{r}
autoplot(ts_w, ylab = "Index") + autolayer(ts_w) + autolayer(ts_a) + autolayer(ts_t) + autolayer(ts_r) + labs(colour = "transport") + scale_color_manual(labels = c("Plane","Railway","Truck","Ship"), values = c(1,2,3,4))
ggsubseriesplot(ts_w)
ggsubseriesplot(ts_a)
ggsubseriesplot(ts_t)
ggsubseriesplot(ts_r)
ggAcf(ts_w)
ggAcf(ts_a)
ggAcf(ts_t)
ggAcf(ts_r)
Box.test(ts_w,type = "Ljung-Box")
Box.test(ts_a,type = "Ljung-Box")
Box.test(ts_t,type = "Ljung-Box")
Box.test(ts_r,type = "Ljung-Box")
plot(decompose(ts_w, type = "additive"))
plot(decompose(ts_a, type = "additive"))
plot(decompose(ts_t, type = "additive"))
plot(decompose(ts_r, type = "additive"))
```
While it seems that the shipments by sea and by air have ACF plots that rapidly decrease to 0, the truck and railway ACF plots decrease more slowly which means they are not stationary.

```{r}
ndiffs(ts_w_train)
ndiffs(ts_a_train)
ndiffs(ts_t_train)
ndiffs(ts_r_train)

nsdiffs(ts_w_train)
nsdiffs(ts_a_train)
nsdiffs(ts_t_train)
nsdiffs(ts_r_train)
```
With `ndiffs()` it seems all the time series need one differencing. But no seasonal differencing is needed.

```{r}
autofit <- auto.arima(ts_w_train)
autofit2 <- auto.arima(ts_a_train)
autofit3 <- auto.arima(ts_t_train)
autofit4 <- auto.arima(ts_r_train)
```

```{r}
ggtsdisplay(diff(ts_w_train)) # either AR(2) or MA(1)
ggtsdisplay(diff(ts_a_train)) # either AR(1) or MA(1)
ggtsdisplay(diff(ts_t_train)) # AR(1) or MA(1)
ggtsdisplay(diff(ts_r_train)) #AR or MA(1)
```

```{r}
manfit <- Arima(ts_w_train, order = c(2,1,0))
manfit1 <- Arima(ts_w_train, order = c(0,1,1))
manfit2 <- Arima(ts_a_train, order = c(1,1,0))
manfit22 <- Arima(ts_a_train, order = c(0,1,1))
manfit3 <- Arima(ts_t_train, order = c(1,1,0))
manfit33 <- Arima(ts_t_train, order = c(0,1,1))
manfit4 <- Arima(ts_r_train, order = c(1,1,0))
manfit44 <- Arima(ts_r_train, order = c(0,1,1))
```

```{r}
autofit$aicc < manfit$aicc
autofit$aicc < manfit1$aicc
autofit2$aicc < manfit2$aicc
autofit2$aicc < manfit22$aicc
autofit3$aicc < manfit3$aicc
autofit3$aicc < manfit33$aicc
autofit4$aicc < manfit4$aicc
autofit4$aicc < manfit44$aicc
```
Overall, it seems that the `auto.arima()` function picked most of the models with the lowest AICc.




```{r}
checkresiduals(manfit1)
checkresiduals(autofit2)
checkresiduals(autofit3)
checkresiduals(autofit4)
```
THe first Ljung-Box test does not pass--it's white noise. The others do pass and are white noise.


```{r}
test_w <- window(ts_w, start = 2013)
test_a <- window(ts_a, start = 2013)
test_t <- window(ts_t, start = 2013)
test_r <- window(ts_r, start = 2013)



accuracy(forecast(manfit1, h = 72), test_w)
accuracy(forecast(autofit2, h = 72), test_a)
accuracy(forecast(autofit3, h = 72), test_t)
accuracy(forecast(autofit4, h = 72), test_r)
```

