---
title: 'Forecasting Time Series Models: Problem Set 2'
author: "Your name goes here"
date: "Due: Feb 17, 2019"
---
```{r, warning = FALSE, message = FALSE}
library(fpp2) # You will always load this package before analyzing any time series data.
```

### Question 1: 

Calculate the residuals from a seasonal naive forecast applied to the quarterly Australian beer production data from 1992. The following code will help.

```{r, eval=FALSE} 
# You need to turn eval=TRUE for the code to be evaluated.
beer <- window(ausbeer, start=1992) 
fc_beer <- beer %>% 
  snaive()    # Use seasonal naive method to forcaste the beer production

fc_beer %>%
  autoplot()  # Plot seasonal naive forecasts

res <- fc_beer %>%
  residuals() # Compute residuals of beer data set obtained from seasonal naive method 
  
autoplot(res) # Plot residuals
```


Test if the residuals are white noise and normally distributed.
```{r} 
# Your R code goes here
```
    Q: What do you conclude?
    Your comments go here.


### Question 2:
Consider the daily closing IBM stock prices (data set `ibmclose`).

- What is this data about? (hint: you can use `?ibmclose`)
- Produce some plots of the data in order to become familiar with it.
- Split the data into a training set of 300 observations and a test set of 69 observations.
- Try using various benchmark methods to forecast the training set and compare the results on the test set. Which method did best?
- Check the residuals of your preferred method. Do they resemble white noise?

### Question 3:
Consider the sales of new one-family houses in the USA, Jan 1973 to Nov 1995 (data set `hsales`)

- What is this data about? 
- Produce some plots of the data in order to become familiar with it.
- Split the `hsales` data set into a training set and a test set, where the test set is the last two years of data.
- Try using various benchmark methods to forecast the training set and compare the results on the test set. Which method did best?
- Check the residuals of your preferred method. Do they resemble white noise?


