---
title: 'Forecasting Time Series Models: Problem Set 1'
author: "Hannah Laws"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---
```{r, warning = FALSE, message = FALSE}
library(fpp2) # You will always load this package before analyzing any time series data.
```

### Question 1: 
Download the file `tute1.csv` from [http://robjhyndman.com/data/tute1.csv](http://robjhyndman.com/data/tute1.csv), open it in Excel (or some other spreadsheet application), and review its contents. You should find four columns of information. Columns B through D each contain a quarterly series, labelled Sales, AdBudget and GDP. Sales contains the quarterly sales for a small company over the period 1981-2005. AdBudget is the advertising budget and GDP is the gross domestic product. All series have been adjusted for inflation.

a - You can read the data into R with the following script:
```{r}
tute1 <- read.csv("http://robjhyndman.com/data/tute1.csv", header=TRUE) 
# Directly download file to R from internet. 

# or you can read your file from your computer using read.csv function
# tute1 <- read.csv("C:/Users/arifi/Downloads/tute1.csv")

```

b - Convert the data to time series
```{r}
mytimeseries <- ts(tute1[,-1], start=1981, frequency=4)
# The [,-1] removes the first column which contains the quarters as we do not need them now.
```

c - Construct time series plots of each of the three series
```{r, eval=TRUE}
# You need to either delete or turn eval=TRUE for this code to be evaluated.
autoplot(mytimeseries, facets=TRUE)
```

Check what happens when you do not include facets=TRUE.

### Question 2: 

Use the the following graphics functions: `autoplot`, `ggseasonplot`, `ggsubseriesplot`, `gglagplot`, `ggAcf` and explore features from the following time series: `hsales`, `usdeaths`, `bricksq`, `sunspotarea`, `gasoline`.

```{r}
# Replace this comment with R code to achieve the above tasks.
# Hint: apply each function to each time series; autoplot(mydata), ggAcf(mydata2), etc.
autoplot(hsales)
ggseasonplot(hsales)
ggsubseriesplot(hsales)
gglagplot(hsales)
ggAcf(hsales)


```

```{r}
# Next graph goes here. 
autoplot(usdeaths)
ggseasonplot(usdeaths)
ggsubseriesplot(usdeaths)
gglagplot(usdeaths)
ggAcf(usdeaths)
```

```{r}
# Next graph goes here. Copy and paste for each additional graph.
autoplot(bricksq)
ggseasonplot(bricksq)
ggsubseriesplot(bricksq)
gglagplot(bricksq)
ggAcf(bricksq)
```

```{r}
# Next graph goes here. Copy and paste for each additional graph.
autoplot(sunspotarea)
ggseasonplot(sunspotarea)
ggsubseriesplot(sunspotarea)
gglagplot(sunspotarea)
ggAcf(sunspotarea)
```

- For each series, can you spot any seasonality, cyclicity and trend?
- What do you learn about the series?

### Question 3: 

`dj` contains 292 consecutive trading days of the Dow Jones Index. Use `ddj <- diff(dj)` to compute the daily changes in the index. Plot `ddj` and its ACF. Do the changes in the Dow Jones Index look like white noise?

```{r}
# Next R code goes here. Copy and paste for each additional code chunk.
ddj <- diff(dj)
ggAcf(ddj)
```

Considering that the lags do not exceed the base parameters, these changes in the Dow Jones Index look like white noise.

### Question 4:

The `pigs` data shows the monthly total number of pigs slaughtered in Victoria, Australia, from Jan 1980 to Aug 1995. Use `mypigs <- window(pigs, start=1990)` to select the data starting from 1990. Use `autoplot` `Ljung Box test`, and `ggAcf` for `mypigs` series and compare these to white noise plots from Figures `2.15` and `2.16` in the textbook.

```{r}
#  Next R code goes here. Copy and paste for each additional code chunk.
mypigs <- window(pigs, start = 1990)
autoplot(mypigs)
Box.test(ts(mypigs),lag = 20, type = "Lj")
ggAcf(mypigs)

```

## How to upload this file on AsUlearn?

When you are ready to upload this assignment

- Click dropdown menu from `Knit`.
- Then click `Knit to HTML`.
- Open the pop-up file and click `Open in Browser`.
- Press the `ctrl+S`.
- Save the file as `YourName_PS1`.
- Upload `YourName_PS1` to `AsUlearn`. 
