---
title: 'Forecasting Time Series Models: Problem Set 1'
author: "Hannah Laws"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---
```{r, warning = FALSE, message = FALSE}
library(fpp2)
```

### Question 1: 
Download the file `tute1.csv` from [http://robjhyndman.com/data/tute1.csv](http://robjhyndman.com/data/tute1.csv), open it in Excel (or some other spreadsheet application), and review its contents. You should find four columns of information. Columns B through D each contain a quarterly series, labelled Sales, AdBudget and GDP. Sales contains the quarterly sales for a small company over the period 1981-2005. AdBudget is the advertising budget and GDP is the gross domestic product. All series have been adjusted for inflation.

A - You can read the data into R with the following script:
```{r}
tute1 <- read.csv("http://robjhyndman.com/data/tute1.csv", header=TRUE) 
```

B - Convert the data to time series
```{r}
mytimeseries <- ts(tute1[,-1], start=1981, frequency=4)
```

C - Construct time series plots of each of the three series
```{r, eval=TRUE, echo=FALSE}
autoplot(mytimeseries, facets=TRUE)
autoplot(mytimeseries)

```

When including facets = T, each of the variables in the time series will be plotted on separate graphs. If the facets = F, then the variables will all be plotted on the same graph in different colors to differentiate them.


### Question 2: 

Use the the following graphics functions: `autoplot`, `ggseasonplot`, `ggsubseriesplot`, `gglagplot`, `ggAcf` and explore features from the following time series: `hsales`, `usdeaths`, `bricksq`, `sunspotarea`, `gasoline`.

##hsales
```{r, echo = F}
autoplot(hsales)
ggseasonplot(hsales)
ggsubseriesplot(hsales)
gglagplot(hsales)
ggAcf(hsales)
```

The hsales data seems to have a seasonality to it.

##usdeaths
```{r, echo=F}
autoplot(usdeaths)
ggseasonplot(usdeaths)
ggsubseriesplot(usdeaths)
gglagplot(usdeaths)
ggAcf(usdeaths)
```

usdeaths definitely has a yearly seasonalit, but no trend of cyclic behavior.

##bricksq
```{r, eval = T, echo = F}
autoplot(bricksq)
ggseasonplot(bricksq)
ggsubseriesplot(bricksq)
gglagplot(bricksq)
ggAcf(bricksq)
```

bricksq has a increasing trend with a quarterly seasonality.

##sunspotarea
```{r}
autoplot(sunspotarea)
# ggseasonplot(sunspotarea)
# ggsubseriesplot(sunspotarea)
gglagplot(sunspotarea)
ggAcf(sunspotarea)
```

sunspotarea appears to be cyclical. There were also errors when conducting the `ggseasonalplot` and `ggsubseriesplot` functions because R did not see this dataset having any seasonality.


- For each series, can you spot any seasonality, cyclicity and trend?
- What do you learn about the series?

### Question 3: 

`dj` contains 292 consecutive trading days of the Dow Jones Index. Use `ddj <- diff(dj)` to compute the daily changes in the index. Plot `ddj` and its ACF. Do the changes in the Dow Jones Index look like white noise?

```{r, echo = FALSE}
ddj <- diff(dj)
ggAcf(ddj)
```

Considering that the lags do not exceed the base parameters, these changes in the Dow Jones Index look like white noise.

### Question 4:

The `pigs` data shows the monthly total number of pigs slaughtered in Victoria, Australia, from Jan 1980 to Aug 1995. Use `mypigs <- window(pigs, start=1990)` to select the data starting from 1990. Use `autoplot` `Ljung Box test`, and `ggAcf` for `mypigs` series and compare these to white noise plots from Figures `2.15` and `2.16` in the textbook.

```{r, echo = FALSE}
mypigs <- window(pigs, start = 1990)
autoplot(mypigs)
Box.test(ts(mypigs),lag = 20, type = "Lj")
ggAcf(mypigs)

```

The `mypigs` data has no establish seasonal pattern as the data in Figure 2.15. The ACF also shows no trend or seasonality compared to Figure `2.16`. Most of the lags do not even reach past the calculated threshold to be significant. 


```{r, eval=FALSE, echo=FALSE}
## How to upload this file on AsUlearn?

When you are ready to upload this assignment

- Click dropdown menu from `Knit`.
- Then click `Knit to HTML`.
- Open the pop-up file and click `Open in Browser`.
- Press the `ctrl+S`.
- Save the file as `YourName_PS1`.
- Upload `YourName_PS1` to `AsUlearn`. 

```

