---
title: 'Forecasting Time Series Models: Problem Set 3'
subtitle: "Linear regression models"
author: "Your name/s here"
date: "Date: "
---
```{r, warning = FALSE, message = FALSE}
library(fpp2) # You will always load this package before analyzing any time series data.
library(lmtest)
```

### Question: 

You own a shop that sells gifts, souvenirs, and novelties. The shop, opened in January 1987, is situated on the wharf at a beach resort town in Queensland, Australia. The sales volume varies with the seasonal population of tourists. There is a massive influx of visitors to the town at Christmas and for the local surfing festival, held every March since 1988. 

You are interested in expanding the premises, the range of products, and staff overtime. To extend your business, you need to forecast future sales.
The data set `fancy` concerns the monthly sales figures for this shop.

1- Produce a time plot of the data and describe the patterns in the graph. Identify any unusual or unexpected fluctuations in the time series.
```{r}
autoplot(fancy)
ggseasonplot(fancy)
ggsubseriesplot(fancy)
ggAcf(fancy)
Box.test(fancy,type = "Ljung-Box")
plot(decompose(fancy, type = "multiplicative"))
```
From the plot of the original series, it would seem that this data have an increasing trend with seassonality. With the decomposition of the series, this further confirms an upward trend and seasonality. However, looking at the ACF lag plot, it looks as though there is is not much significance in the data. And with the Ljung-Box test having a small p-value, this brings even more concern that the series may be white noise.   

2- Explain why it is necessary to take logarithms of these data before fitting a model.
With the positive trend in the data, we would want the logarithms of the data to take out the trend and focus on the seasonal nature of the data.

3- Use R to fit a regression model to the logarithms of these sales data with a linear trend, seasonal dummies and a *surfing festival* dummy variable.
```{r}
surf.fest <- cycle(fancy)==3
surf.fest[3] <- FALSE
mod <- tslm(log(fancy) ~ trend + season + surf.fest, data = fancy)
summary(mod)
```


4- Plot the residuals against time and against the fitted values. Do these plots reveal any problems with the model?
```{r}
res <- residuals(mod)
autoplot(res)
ggplot(fancy,aes(x = res, y = fitted(mod))) + geom_point()
checkresiduals(mod)
```
The plots do not seem to show any indication of a pattern. Using the `checkresiduals` command also confirms that the residuals are just barely white noise. Many of the ACF lags reach past the threshold so while there technically is nothing left in the residuals, it's a pretty close call.

5- Do boxplots of the residuals for each month. Does this reveal any problems with the model?
```{r}
boxplot(residuals(mod)~cycle(residuals(mod)))
```
Looking at the boxplots of the residuals for each month, there seems to be larger difference in variance in the colder months such as August through December. This should not be the case if the model fits the data well, so this further confirms that it is missing information.


6- What do the values of the coefficients tell you about each variable?
Each of the coefficients represent the percentage change in sales in relation to a unit change in the variable. So if `season2` were to increase by one unit, then the sales will change by roughly 0.25%. Since most of the coefficients are relatively small, this would mean that they do not have a big impact on sales.

7- What does the Breusch-Godfrey test tell you about your model?
```{r}
bgtest(mod, fill = NA)
```
The Breusch-Godfrey test gives a p-value of 3.795e-07 which means the null hypothesis is reject. So there is serial correlation in the model. 

8- Regardless of your answers to the above questions, use a regression model to predict the monthly sales for 1994, 1995, and 1996. Produce prediction intervals for each of your forecasts.
```{r}
pred <- forecast(mod,newdata = data.frame(surf.fest = rep(FALSE,36)))
pred
```


9- How could you improve these predictions by modifying the model?
According to the Breusch-Godfrey test indicating that there is serial correlation in the model, it would be best to capture this information to improve the model. This can be acheived by taking the log of all variables, or ridding of seasonality.





